\textls{Large-Scale Content-Based Matching of MIDI and Audio Files}

### 2015-07-16 paper.tex
Make title fit in one line
Add note about Whetlab disappearing

\documentclass{article}
\usepackage{ismir,amsmath,cite}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{color}
\usepackage{framed}
\usepackage{booktabs}

\title{Large-Scale Content-Based Matching of MIDI and Audio Files}

@@

To ensure good performance, we optimized all model hyperparameters using Whetlab,\footnote{\texttt{http://www.whetlab.com}} a web API which implements black-box Bayesian optimization \cite{snoek2012practical}.
We used Whetlab to optimize the number of convolutional/pooling layers, the number and size of the fully-connected layers, the RMSProp learning rate and decay parameters, and the $\alpha$ and $m$ regularization parameters of $\mathcal{L}$.
As a hyperparameter optimization objective, we used the Bhattacharyya distance as described above.
The best performing network found by Whetlab had 2 convolutional layers, 2 ``hidden'' fully-connected layers with 2048 units in addition to a fully-connected output layer, a learning rate of .001 with a decay parameter of .65, $\alpha = .5$, and $m = 4$.
This hyperparameter configuration yielded the output hash distance distributions for $\mathcal{P}$ and $\mathcal{N}$ shown in Figure \ref{fig:distances}, for a Bhattacharyya separation of $0.488$.

>>>>

\documentclass{article}
\usepackage{ismir,amsmath,cite}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{color}
\usepackage{framed}
\usepackage{booktabs}
\usepackage[letterspace=-22]{microtype}

\title{\textls{Large-Scale Content-Based Matching of MIDI and Audio Files}}

@@

To ensure good performance, we optimized all model hyperparameters using Whetlab,\footnote{Between submission and acceptance of this paper, Whetlab announced it would be ending its service.  For posterity, the results of our hyperparameter search are available at \texttt{http://bit.ly/hash-param-search}.} a web API which implements black-box Bayesian optimization \cite{snoek2012practical}.
We used Whetlab to optimize the number of convolutional/pooling layers, the number and size of the fully-connected layers, the RMSProp learning rate and decay parameters, and the $\alpha$ and $m$ regularization parameters of $\mathcal{L}$.
As a hyperparameter optimization objective, we used the Bhattacharyya distance as described above.
The best performing network found by Whetlab had 2 convolutional layers, 2 ``hidden'' fully-connected layers with 2048 units in addition to a fully-connected output layer, a learning rate of .001 with a decay parameter of .65, $\alpha = .5$, and $m = 4$.
This hyperparameter configuration yielded the output hash distance distributions for $\mathcal{P}$ and $\mathcal{N}$ shown in Figure \ref{fig:distances}, for a Bhattacharyya separation of $0.488$.
